---
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r message=FALSE}
library(sde)
library(ggplot2)
library(dplyr)
```

# Black Scholes True solution function
```{r}
sde.bs.true <- function(X0=100, theta=c(0.05, 0.25), delta.t=0.004, T=1){
  t <- seq(0, T, delta.t)
  dW <- c(0)
  dW <- append(dW, rnorm(T/delta.t, 0, sqrt(delta.t)))
  B <- cumsum(dW)
  return (X0*exp((theta[1]-(theta[2]**2)/2)*t + theta[2]*B))
}
```

# Runge-Kutta function
```{r}
sde.rk <- function(X0=100, theta=c(0.05, 0.25), delta.t=0.004, T=1){
  mu <- theta[1]
  sigma <- theta[2]
  dW <- c(0)
  dW <- append(dW, rnorm(T / delta.t, 0, sqrt(delta.t)))
  t <- seq(0, T, delta.t)
  sde.runge.kutta <- numeric(length(t))
  sde.runge.kutta[1] <- X0
  for (i in 2:length(t)){
    upsilon <- sde.runge.kutta[i-1] + mu*sde.runge.kutta[i-1]*delta.t +
      sigma*sde.runge.kutta[i-1]*sqrt(delta.t)
    
    sde.runge.kutta[i] <- sde.runge.kutta[i-1] + mu*sde.runge.kutta[i-1]*delta.t +
      sigma*sde.runge.kutta[i-1]*dW[i] + 
      0.5*sigma*(upsilon-sde.runge.kutta[i-1])*(dW[i]**2-delta.t)*(delta.t**(-0.5))
  }
  return (sde.runge.kutta)
}
```

# Changing drift function(1% - 10%) with high sigma: Setting up the bounds
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.25
repeat.count <- 5000
mu.lower <- 0.01
mu.upper <- 0.1
mu.delta <- 0.01
mu.list <- seq(mu.lower, mu.upper, mu.delta)
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Changing drift function(1% - 10%) with high sigma: Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
sim.true <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  sim.true <- c(sim.true, replicate(repeat.count, 
              sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma))))
}
```

# Changing drift function(1% - 10%) with high sigma: Monte-Carlo Simulation of Milstein
```{r}
sim.mil <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  d <- parse(text = paste(mu,"* x"))
  s <- parse(text = paste(sigma,"* x"))
  s.x <- parse(text = paste(sigma))
  sim.mil <- c(sim.mil, replicate(repeat.count, 
              sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                       method="milstein", N=N, T=T)))
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.mil <- data.frame(mu=dummy.mu,
                         method=rep("mil",repeat.count*(N+1)*length(mu.list)),
                        err=sim.mil-sim.true, abs.err=abs(sim.mil-sim.true))
```

# Changing drift function(1% - 10%) with high sigma: Monte-Carlo Simulation of Second Milstein Scheme
```{r}
sim.mil2 <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  d <- parse(text = paste(mu,"* x"))
  s <- parse(text = paste(sigma,"* x"))
  d.x <- parse(text = paste(mu))
  s.x <- parse(text = paste(sigma))
  d.xx <- parse(text = paste(0))
  s.xx <- parse(text = paste(0))
  sim.mil2 <- c(sim.mil2, replicate(repeat.count, 
              sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                      drift.xx = d.xx, sigma.xx = s.xx, 
                      method="milstein2", N=N, T=T)))
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.mil2 <- data.frame(mu=dummy.mu, 
                          method=rep("mil2",repeat.count*(N+1)*length(mu.list)),
                        err=sim.mil2-sim.true, abs.err=abs(sim.mil2-sim.true))
```

# Changing drift function(1% - 10%) with high sigma: Monte-Carlo Simulation of Runge-Kutta
```{r}
sim.rk <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  sim.rk <- c(sim.rk, replicate(repeat.count, 
              sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
              )
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.rk <- data.frame(mu=dummy.mu, 
                        method=rep("rk",repeat.count*(N+1)*length(mu.list)),
                        err=sim.rk-sim.true, abs.err=abs(sim.rk-sim.true))
```

# Changing drift function(1% - 10%) with high sigma: Mean and Confident Interval of Absolute Errors
```{r}
conf.int.mil <- aggregate(df.err.mil$abs.err, list(df.err.mil$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
conf.int.mil2 <- aggregate(df.err.mil2$abs.err, list(df.err.mil2$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
conf.int.rk <- aggregate(df.err.rk$abs.err, list(df.err.rk$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
mean.mil <- aggregate(df.err.mil$abs.err, list(df.err.mil$mu), FUN=mean)
mean.mil2 <- aggregate(df.err.mil2$abs.err, list(df.err.mil2$mu), FUN=mean)
mean.rk <- aggregate(df.err.rk$abs.err, list(df.err.rk$mu), FUN=mean)

mean.mil
mean.mil2
mean.rk
conf.int.mil$x
conf.int.mil2$x
conf.int.rk$x
```

# Changing drift function(1% - 10%) with high sigma: Plot the results
```{r warning=FALSE}
df.err <- rbind(df.err.mil, df.err.mil2, df.err.rk)
df.err$mu <- factor(df.err$mu)

p <-df.err %>%
  mutate() %>%
  ggplot( aes(x=mu, y=abs.err, fill=method) ) +
    geom_boxplot(outlier.shape=NA) +
    ggtitle("Varying Interest (1% - 10%)") +
    xlab("Interest Rate") +
    ylab("Absolute Error") +
    stat_summary(fun = median,
               geom = "line",
               aes(group = method, color = method)) +
    scale_fill_discrete(labels=c('Milstein Scheme',
                                 'Second Milstein Scheme', 
                                 'Runge-Kutta Method'))+
    scale_color_discrete(labels=c('Milstein Scheme',
                                  'Second Milstein Scheme', 
                                  'Runge-Kutta Method'))+
    guides(fill=guide_legend(title="Method"), 
           color=guide_legend(title="Method")) +
    scale_x_discrete(labels = mu.list)+
    scale_y_continuous(limits = c(0, 0.12))
p
```

# Changing drift function(1% - 10%) with low sigma: Setting up the bounds
```{r}
sigma <- 0.01
mu.lower <- 0.01
mu.upper <- 0.1
mu.delta <- 0.01
mu.list <- seq(mu.lower, mu.upper, mu.delta)
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Changing drift function(1% - 10%) with low sigma: Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
sim.true <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  sim.true <- c(sim.true, replicate(repeat.count, 
              sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma))))
}
```

# Changing drift function(1% - 10%) with low sigma: Monte-Carlo Simulation of Milstein
```{r}
sim.mil <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  d <- parse(text = paste(mu,"* x"))
  s <- parse(text = paste(sigma,"* x"))
  s.x <- parse(text = paste(sigma))
  sim.mil <- c(sim.mil, replicate(repeat.count, 
              sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                       method="milstein", N=N, T=T)))
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.mil <- data.frame(mu=dummy.mu,
                         method=rep("mil",repeat.count*(N+1)*length(mu.list)),
                        err=sim.mil-sim.true, abs.err=abs(sim.mil-sim.true))
```

# Changing drift function(1% - 10%) with low sigma: Monte-Carlo Simulation of Second Milstein Scheme
```{r}
sim.mil2 <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  d <- parse(text = paste(mu,"* x"))
  s <- parse(text = paste(sigma,"* x"))
  d.x <- parse(text = paste(mu))
  s.x <- parse(text = paste(sigma))
  d.xx <- parse(text = paste(0))
  s.xx <- parse(text = paste(0))
  sim.mil2 <- c(sim.mil2, replicate(repeat.count, 
              sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                      drift.xx = d.xx, sigma.xx = s.xx, 
                      method="milstein2", N=N, T=T)))
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.mil2 <- data.frame(mu=dummy.mu, 
                          method=rep("mil2",repeat.count*(N+1)*length(mu.list)),
                        err=sim.mil2-sim.true, abs.err=abs(sim.mil2-sim.true))
```

# Changing drift function(1% - 10%) with low sigma: Monte-Carlo Simulation of Runge-Kutta
```{r}
sim.rk <- numeric(0)
dummy.mu <- numeric(0)
set.seed(seed)
for (mu in mu.list) {
  sim.rk <- c(sim.rk, replicate(repeat.count, 
              sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
              )
  dummy.mu <- c(dummy.mu, rep(mu, repeat.count*(N+1)))
}
df.err.rk <- data.frame(mu=dummy.mu, 
                        method=rep("rk",repeat.count*(N+1)*length(mu.list)),
                        err=sim.rk-sim.true, abs.err=abs(sim.rk-sim.true))
```

# Changing drift function(1% - 10%) with low sigma: Mean and Confident Interval of Absolute Errors
```{r}
conf.int.mil <- aggregate(df.err.mil$abs.err, list(df.err.mil$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
conf.int.mil2 <- aggregate(df.err.mil2$abs.err, list(df.err.mil2$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
conf.int.rk <- aggregate(df.err.rk$abs.err, list(df.err.rk$mu), 
                        FUN=quantile, probs=c(0.025, 0.975))
mean.mil <- aggregate(df.err.mil$abs.err, list(df.err.mil$mu), FUN=mean)
mean.mil2 <- aggregate(df.err.mil2$abs.err, list(df.err.mil2$mu), FUN=mean)
mean.rk <- aggregate(df.err.rk$abs.err, list(df.err.rk$mu), FUN=mean)

mean.mil
mean.mil2
mean.rk
conf.int.mil$x
conf.int.mil2$x
conf.int.rk$x
```

# Changing drift function(1% - 10%) with low sigma: Plot the results
```{r warning=FALSE}
df.err <<- rbind(df.err.mil, df.err.mil2, df.err.rk)
df.err$mu <- factor(df.err$mu)

p <-df.err %>%
  mutate() %>%
  ggplot( aes(x=mu, y=abs.err, fill=method) ) +
    geom_boxplot(outlier.shape=NA) +
    ggtitle("Varying Interest (1% - 10%)") +
    xlab("Interest Rate") +
    ylab("Absolute Error") +
    stat_summary(fun = median,
               geom = "line",
               aes(group = method, color = method)) +
    scale_fill_discrete(labels=c('Milstein Scheme',
                                 'Second Milstein Scheme', 
                                 'Runge-Kutta Method'))+
    scale_color_discrete(labels=c('Milstein Scheme',
                                  'Second Milstein Scheme', 
                                  'Runge-Kutta Method'))+
    guides(fill=guide_legend(title="Method"), 
           color=guide_legend(title="Method")) +
    scale_x_discrete(labels = mu.list)
p
```









