---
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
```{r message=FALSE}
library(sde)
library(ggplot2)
library(dplyr)
```

# Black Scholes True solution function
```{r}
sde.bs.true <- function(X0=100, theta=c(0.05, 0.25), delta.t=0.004, T=1){
  t <- seq(0, T, delta.t)
  dW <- c(0)
  dW <- append(dW, rnorm(T/delta.t, 0, sqrt(delta.t)))
  B <- cumsum(dW)
  return (X0*exp((theta[1]-(theta[2]**2)/2)*t + theta[2]*B))
}
```

# Runge-Kutta function
```{r}
sde.rk <- function(X0=100, theta=c(0.05, 0.25), delta.t=0.004, T=1){
  mu <- theta[1]
  sigma <- theta[2]
  dW <- c(0)
  dW <- append(dW, rnorm(T / delta.t, 0, sqrt(delta.t)))
  t <- seq(0, T, delta.t)
  sde.runge.kutta <- numeric(length(t))
  sde.runge.kutta[1] <- X0
  for (i in 2:length(t)){
    upsilon <- sde.runge.kutta[i-1] + mu*sde.runge.kutta[i-1]*delta.t +
      sigma*sde.runge.kutta[i-1]*sqrt(delta.t)
    
    sde.runge.kutta[i] <- sde.runge.kutta[i-1] + mu*sde.runge.kutta[i-1]*delta.t +
      sigma*sde.runge.kutta[i-1]*dW[i] + 
      0.5*sigma*(upsilon-sde.runge.kutta[i-1])*(dW[i]**2-delta.t)*(delta.t**(-0.5))
  }
  return (sde.runge.kutta)
}
```

# Setting up the parameters for simulations - sigma = 1%
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.01
mu <- 0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
     xlim= c(-0.005, 0.005), main = 'Distribution of Errors', 
     sub='sigma=0.01', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topleft', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```

# Setting up the parameters for simulations - sigma = 5%
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.05
mu <- 0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
     xlim= c(-0.01, 0.01), ylim=c(0, 800),
     main = 'Distribution of Errors', 
     sub='sigma=0.05', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topleft', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```

# Setting up the parameters for simulations - sigma = 15%
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.15
mu <- 0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
     xlim= c(-0.03, 0.03), ylim = c(0, 300),
     main = 'Distribution of Errors', 
     sub='sigma=0.15', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topleft', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```

# Setting up the parameters for simulations - sigma = 30%
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.30
mu <- 0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
     xlim= c(-0.1, 0.2), ylim = c(0, 150),
     main = 'Distribution of Errors', 
     sub='sigma=0.30', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topright', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```

# Setting up the parameters for simulations - sigma = 5%, negative mu
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.05
mu <- -0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
      xlim= c(-0.01, 0.01), ylim = c(0, 800),
     main = 'Distribution of Errors', 
     sub='sigma=0.05', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topleft', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```


# Setting up the parameters for simulations - sigma = 30%, negative mu
```{r}
seed <- 20230331
T <- 1
N <- 250 * T
delta <- T/N
sigma <- 0.30
mu <- -0.05
repeat.count <- 5000
df.err <- data.frame(mu=numeric(0), method=character(0), 
                     err=numeric(0), abs.err=numeric(0))
```

# Monte-Carlo Simulation of Black-Scholes True Solution
```{r}
set.seed(seed)
sim.true <- replicate(repeat.count, 
            sde.bs.true(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Monte-Carlo Simulation of Milstein
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
s.x <- parse(text = paste(sigma))
sim.mil <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, sigma.x = s.x,
                     method="milstein", N=N, T=T))
```

# Monte-Carlo Simulation of Second Milstein Scheme
```{r}
set.seed(seed)
d <- parse(text = paste(mu,"* x"))
s <- parse(text = paste(sigma,"* x"))
d.x <- parse(text = paste(mu))
s.x <- parse(text = paste(sigma))
d.xx <- parse(text = paste(0))
s.xx <- parse(text = paste(0))
sim.mil2 <- replicate(repeat.count, 
            sde.sim(X0=100, drift=d, sigma=s, drift.x=d.x, sigma.x = s.x,
                    drift.xx = d.xx, sigma.xx = s.xx, 
                    method="milstein2", N=N, T=T))
```

# Monte-Carlo Simulation of Runge-Kutta
```{r}
set.seed(seed)
sim.rk <- replicate(repeat.count, 
            sde.rk(T=T, delta.t = T/N, theta=c(mu,sigma)))
```

# Plot the distribution of the errors
```{r}
plot(density(sim.mil2 - sim.true), col="green", 
      xlim= c(-0.2, 0.1), ylim = c(0, 150),
     main = 'Distribution of Errors', 
     sub='sigma=0.30', xlab='Error')
lines(density(sim.mil - sim.true), col="red")
lines(density(sim.rk - sim.true), col="blue")
legend('topleft', legend=c("Milstein", "Second Milstein", "Runge-Kutta"),
       col=c("red", "green" ,"blue"), lty=1, cex=0.8)
```



